An efficient acyclic contact planner for multiped robots

### 2016-01-03 body/appendix_roms.tex
final version before video inclusion

Figure~\ref{fig:hrp2_roms} illustrate the obtained $W^k$ for HRP-2.
Regarding the procedure, we can see that step 2 is conservative (Figure~\ref{fig:hrp2_roms}--right), which 
is acceptable, especially because the lost set essentially relates to configurations close to singularity (they are close to the boundaries of the reachable workspace). We choose again to be less complete
but more efficient, regarding the number of collision tests to be performed by RB-RRT.
In step 1 on the other hand, selecting the convex hull (Figure~\ref{fig:hrp2_roms}--middle) instead of a minimum encompassing shape (Figure~\ref{fig:hrp2_roms}--left) may introduce false positives.
Concretely, because the false positive set intersects with $W^0$, the scaling volume of the robot torso, the induced error is compensated,
as verified by the date of Table~\ref{tab:requestpercent}.

\subsection{Step 2: computing the trunk scaling workspace $W^0$ of the robot}
To define the volume $W^0$ of HRP-2, we proceed in an empirical manner.
First, we compute the bounding boxes of the robot trunk, head, and upper legs (Figure~\ref{fig:hrp2_w} -- red shapes).
Then, we perform a scaling of these boxes by a factor $s$. For different values of $s$, we verify the true feasibility condition:
For a large number of configurati
ons that verify the reachability condition, we try to generate contact configurations. We plot 
the success rates obtained depending on $s$ (Figure~\ref{hrp2_w}). We then choose the minimal satisfying value of $s$.

>>>>

Figure~\ref{fig:hrp2_roms} illustrate the obtained $W^k$ for HRP-2.
Regarding the procedure, we can see that step 2 is conservative (Figure~\ref{fig:hrp2_roms}--right), which 
is acceptable, especially because the lost set essentially relates to configurations close to singularity (they are close to the boundaries of the reachable workspace). We choose again to be less complete
but more efficient, regarding the number of collision tests to be performed by RB-RRT.
In step 1 on the other hand, selecting the convex hull (Figure~\ref{fig:hrp2_roms}--middle) instead of a minimum encompassing shape (Figure~\ref{fig:hrp2_roms}--left) may introduce false positives.
Concretely, because the false positive set intersects with $W^0$, the scaling volume of the robot torso, the induced error is compensated,
as verified by the results shown by Table~\ref{tab:requestpercent}.

\subsection{Step 2: computing the trunk scaling workspace $W^0$ of the robot}
To define the volume $W^0$ of HRP-2, we proceed in an empirical manner.
First, we compute the bounding boxes of the robot trunk, head, and upper legs (Figure~\ref{fig:hrp2_w} -- red shapes).
Then, we perform a scaling of these boxes by a factor $s$. For different values of $s$, we verify the geometrical feasibility condition:
For a large number of configurations that verify the reachability condition, we try to generate contact configurations. We then
empirically select the lowest value of $s$ that provides a reasonnable success rate in all scenarios.
For HRP-2, we choose $s=1.2$. This leads to a success rate higher than 86 \% for all scenarios.

### 2016-01-03 body/conclusion.tex
final version before video inclusion

One direction for future work is to focus on a more accurate formulation of $C_{reach}$ to address 
this limitation.
Our main objective is of course to generate the complete interpolation between the contact sequences.
We have already been able to achieve this for HRP-2 for some of the computed sequences~\citep{Carpentier2016}, but we admit that additional
work is required on the planning side to obtain a seamless workflow. To achieve this, we are currently working on the notion of transition certificate, i.e. formulating
conditions that guarantee that the interpolation between two contact configurations is dynamically feasible.
To achieve this, our objective is to propose a geometric quantification of both the kinematic and dynamic constraints of the problem, expressed
at the center of mass of the robot.
 We are also
working on new heuristics more closely related to the dynamics of the systems (for instance, choose the contacts that minimize the jerk between two contact configurations).
These two points illustrate the need to reduce the distance between the planning and control aspects of multiped locomotion. We believe that one way 
to bridge the gap is to introduce robustness while addressing these two issues.

>>>>

One direction for future work is to focus on a more accurate formulation of $C_{reach}$ to address 
this limitation.
Our main objective is of course to generate the complete interpolation between the contact sequences.
We have already obtained some successes for some of the computed sequences~\citep{Carpentier2016}, but we admit that additional
work is required on the planning side to obtain a seamless workflow. To achieve this, we are currently working on the notion of transition certificate, i.e. formulating
conditions that guarantee that the interpolation between two contact configurations is dynamically feasible.
Our current direction is to propose a geometric quantification of both the kinematic and dynamic constraints of the problem, expressed
at the center of mass of the robot.
 We are also
working on new heuristics more closely related to the dynamics of the systems (for instance, choose the contacts that minimize the jerk between two contact configurations).
These two points illustrate the need to reduce the distance between the planning and control aspects of multiped locomotion. We believe that one way 
to bridge the gap is to introduce robustness while addressing these two issues.

### 2016-01-03 body/intro.tex
final version before video inclusion

It thus appears that an integrated optimization-based approach \citep{Mordatch:2012:DCB:2185520.2185539}, able to generate a locally-optimal, complete trajectory within minutes, currently outperforms
existing planners, decoupled or not. However, recent contributions are able to interpolate dynamically-feasible
trajectories between contact configurations \citep{herzog2015trajectory, Carpentier2016}. \citeauthor{Carpentier2016} are able to achieve this with real-time performances.
To generate the input contact configurations, there is a need for an efficient contact planner, able to break the combinatorial to generate discrete contact sequences rapidly. 
Such a planner holds the promise of a complete real-time multi-contact locomotion system.

@@

This sequential approach is the key to the efficiency of our method, though it can
can result in failures because our assumption is not always true. However, we demonstrate empirically the validity of the approach: the high success rate of our method, combined with the low computation times we obtain, allows us to plan (and re-plan upon failure) multi contact sequences at interactive rates.

@@

In Section~\ref{overview}, we present the general organization of our method. Section~\ref{rbprm} and Section~\ref{sec:contact} present respectively our answer to \Pa and \Pb. In Section~\ref{sec:heuristics}, we present two heuristics used for the selection of a contact configuration. Finally, we propose a complete experimental validation of the planner with three very different kinematic chains (the HRP-2 and HyQ robots, and a three-finger manipulator) in various scenarios,
that complete those presented in the conference paper.
\subsection*{Comparison with our previous work.}
The present paper is an extension of a conference paper to appear in the proceedings of the ISRR'15 conference~\citep{tonneauisrr15}.
The conference paper focuses on the theoretical formulation of the problem, and presents results obtained with virtual avatars.
This extension completes this work with a discussion on the implementation of this theory to real-world robots and problems.
In particular, we introduce a robust balance criterion, designed to ensure the equilibrium of the robot despite bounded error in the contact forces. We also provide details on the HPP implementation
of our contact generation algorithm. Furthermore, our experiments are now applied to real-robot models, namely HRP-2 and HyQ\adnote{cite Semini}. Appendix~\ref{app:rom} describes the generation process
for the robot.

>>>>

It thus appears that an integrated optimization-based approach \citep{Mordatch:2012:DCB:2185520.2185539}, able to generate a locally-optimal, complete trajectory within minutes, currently outperforms
existing planners, decoupled or not. However, recent contributions are able to interpolate dynamically-feasible
trajectories between contact configurations \citep{herzog2015trajectory, Park116, Carpentier2016}. \citeauthor{Carpentier2016} are able to achieve this with real-time performances on the real robot.
To generate the input contact configurations, there is a need for an efficient contact planner, able to break the combinatorial to generate discrete contact sequences rapidly. 
Such a planner holds the promise of a complete real-time multi-contact locomotion system.

@@

This sequential approach is the key to the efficiency of our method, though it
can result in failures because our assumption is not always true. However, we demonstrate empirically the validity of the approach: the high success rate of our method, combined with the low computation times we obtain, allows us to plan (and re-plan upon failure) multi contact sequences at interactive rates.

@@

In Section~\ref{overview}, we present the general organization of our method. Section~\ref{rbprm} and Section~\ref{sec:contact} present respectively our answer to \Pa and \Pb. In Section~\ref{sec:heuristics}, we present two heuristics used for the selection of a contact configuration. Finally, we propose a complete experimental validation of the planner with three very different kinematic chains (the HRP-2 and HyQ robots, and a three-finger manipulator) in various scenarios,
that complete those presented in the conference paper.
\subsection*{Comparison with our previous work.}
The present paper is an extension of a conference paper to appear in the proceedings of the ISRR'15 conference~\citep{tonneauisrr15}.
The conference paper focuses on the theoretical formulation of the problem, and presents results obtained with virtual avatars.
This extension completes this work with a discussion on the implementation of this theory to real-world robots and problems.
In particular, we introduce a robust balance criterion, designed to ensure the equilibrium of the robot despite bounded error in the contact forces. We also provide details on the HPP implementation
of our contact generation algorithm. Furthermore, our experiments are now applied to real-robot models, namely HRP-2 and HyQ~\citep{semini11hyqdesignjsce}. Appendix~\ref{app:rom} describes the generation process
for the robot.

### 2016-01-03 body/rbprm.tex
final version before video inclusion

\subsection{Geometrical feasibility: a compromise reachability condition}
The sufficient condition is not interesting in practice since it leads the solver to lose too many interesting trajectories. The necessary condition is not perfect either, since the first stage of the planner would stop on a guide that is not \textit{geometrical feasible} in practice. It might be possible to find a shape $B$ that is necessary and sufficient; however, it seems intuitively very unlikely in general. The construction of a shape $W^0 \subset B \subset B^{max}$ leading to a necessary and sufficient condition (or the proof of its nonexistence) is out of the scope of this work.

>>>>

\subsection{Geometrical feasibility: a compromise reachability condition}
The sufficient condition is not interesting in practice since it leads the solver to lose too many interesting trajectories. The necessary condition is not perfect either, since the first stage of the planner would stop on a guide that is not \textit{geometrically feasible} in practice. It might be possible to find a shape $B$ that is necessary and sufficient; however, it seems intuitively very unlikely in general. The construction of a shape $W^0 \subset B \subset B^{max}$ leading to a necessary and sufficient condition (or the proof of its nonexistence) is out of the scope of this work.

### 2016-01-03 body/results.tex
final version before video inclusion

\begin{figure}[t]
\centering
  \begin{overpic}[width=1\linewidth]{figures/robots_old}
		%~ \put (5,58) {1)} 
		%~ \put (37,58) {2)} 
		%~ \put (68,58) {3.a)} 
		%~ \put (5,27) {3.b)} 
		%~ \put (37,27) {4.a)} 
		%~ \put (68,27) {4.b)} 
	\end{overpic}
\caption{Virtual avatars in various scenarios demonstrated in our conference paper.}
		   \label{fig:robots_old}
\end{figure}

@@

\begin{figure}
  \centering
  %~ \includegraphics[width=0.6\linewidth]{figures/stair_robust}
  \begin{overpic}[width=0.5\linewidth]{figures/stair_robust}
		\put (17,5) {\small{\color{red}$b_0 = 0.23$}} 
		\put (79,5) {\small{\color{green}$b_0 = 6.16$}} 
		%~ \put (68,58) {3.a)} 
		%~ \put (5,27) {3.b)} 
		%~ \put (37,27) {4.a)} 
		%~ \put (68,27) {4.b)} 
	\end{overpic}
  \caption{
           Evaluation of the robustness $b_0$ of two contact configurations. Although in equilibrium, the left configuration is on the verge of slipping.}
		   \label{fig:stair_comp}
\end{figure}

@@

@@

\subsubsection{HyQ -- Obstacle race (Figure~\ref{fig:HyQ_bridge} and~\ref{fig:HyQ_obs}):}
In this long scene, HyQ is first required to cross a 55-cm large hole; then, to cross a narrow "bridge",  only 25-cm large.

@@

\noindent\textbf{Observations:} Despite the apparent simplicity of the scene, this scenario is the hardest for our planner.
While finding a guide path above the hole is easy for the planner, finding a sequence of contacts that allows for equilibrium is not trivial.
Second, the narrow bridge is hard both for the planner and the contact generator: to make sure that equilibrium is preserved along the traversal,
the bridge must be approached with the right angle.
This can is illustrated in Figure~\ref{fig:HyQ_obs}, where several feet rearrangements are required to cross both obstacles (although the video shows this best).
The planner however succeeds in finding a feasible sequence in the end, again with interactive computation times.

\subsubsection{HRP-2 -- Path re-planning(Figure~\ref{fig:re-planning}):}
In this long scene, HRP-2 plans a path through several obstacles. the scene is edited during the execution of the motion: a stair is added,
some stepping stones are removed, and part of the final staircase is deleted. All these modifications require re-planning.

@@

@@

\begin{table*}
\centering
\footnotesize
\begin{tabular}{ >{\centering\arraybackslash}m{37pt} | >{\centering\arraybackslash}m{57pt} | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{70pt} | >{\centering\arraybackslash}m{73pt} | >{\centering\arraybackslash}m{80pt} | >{\centering\arraybackslash}m{10pt}}
  Scenario (nb steps) &  Complete guide generation & Static equilibrium & Collision & Inverse Kinematics  & Total generation time & Time per step\\
 \hline
   Stairs (18) & 6 -- \textbf{13} --  24 & 13 --  \textbf{32} -- 329   & 1 --  \textbf{4} -- 38 & 26 --  \textbf{127} -- 1345 & 92 --  \textbf{261} -- 2174 & \textbf{14} \\
   Standing (24)& 4 -- \textbf{451} --  985 & 27 --  \textbf{144} -- 338   & 2 --  \textbf{12} -- 37 & 144 --  \textbf{1046} -- 2374 & 310 --  \textbf{1622} -- 3429 & \textbf{66}  \\
   Rubble (71)& 3 -- \textbf{524} --  993 & 242 --  \textbf{511} -- 3480   & 233 --  \textbf{505} -- 4564 & 180 --  \textbf{414} -- 3518 & 1400 --  \textbf{3058} -- 13126 & \textbf{43} \\
   Race (112)& 1 -- \textbf{501} --  995 & 266 --  \textbf{449} -- 3956   & 824 --  \textbf{1061} -- 2130 & 666 --  \textbf{874} -- 1613 & 2530 --  \textbf{3722} -- 10030 & \textbf{33} \\
   %Standing up & $70$ & 23 & 48\\
 \end{tabular}
\caption{minimum, \textbf{average} and worst time (in ms) spent in the generation process for each scenario and each critical part of the generation process. The last
column indicates the average time necessary to compute one contact transition.}
\label{tab:requestime}
\quad
\end{table*}

Considering the repartition of the computation time, for HRP-2, most of the time is spent performing inverse kinematics.
This is not surprising considering the number of calls to the methods: IK projection is used intensively to maintain contact continuity between two postures; 
it is also applied every time a new candidate needs to be evaluated. In particular for the standing up scenario,
the kinematic constraints are really strong. Therefore a large number of projections fail because of joint limits violation.

@@

\subsubsection{Success rates}
Table~\ref{tab:requestpercent} summarizes the success rates obtained for each scenario.
\begin{table*}
\centering
\begin{tabular}{ l | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{65pt} | c}
  &  Path planning & True feasibility & Kinematic failure & Equilibrium failure \\
 \hline
   Steep stairs & 100\%  & 99.5\% & 0.11\% & 0.39\% \\
   Standing up & 68\% & 88\% & 6\% & 6\% \\
   %~ Truck egress & \% & \% & \% &  \% \\
   Rubble & 74\% & 97.87\% & 0.13\% & 2\% \\
   Obstacle race & 58\% & 95.7\% & 1.8\% & 2.5\% \\
 \end{tabular}
\caption{Success rates for each scenario. The first value indicates the percentage of successful complete contact plannings for 1000 tests; The second value
indicates the percentage of truly feasible root configurations: considering each limb individually, indicates the percentage of root placements of the guide trajectory that
led to a feasible contact. Kinematic failure is the percentage of contact generations that failed because no collision-free candidate was found. Equilibrium failure is the percentage of contact
generations that failed because no candidate respected the static equilibrium condition.}
\label{tab:requestpercent}
\quad
\end{table*}

We observe that, as expected, our planner does not succeed systematically, because of the approximations made in the implementation
of our theoretical formulation. 
From a pragmatic point of view, regarding the computation times, we claim that our approach is the best current compromise between completeness and efficiency.
Indeed, the advantage of the framework is that when the contact generation fails, it does so rapidly, which allows us to rapidly re-plan a new contact sequence with a reasonable chance of success.
The most efficient (and immediate) approach is probably to launch in parallel several instances of the planner for a given problem (our current implementation is single threaded) and to apply any successful result.

>>>>

\begin{figure}[t]
\centering
  \begin{overpic}[width=1\linewidth]{figures/robots_old}
		%~ \put (5,) {1)} 
		%~ \put (37,) {2)} 
		%~ \put (68,) {3.a)} 
		%~ \put (5,27) {3.b)} 
		%~ \put (37,27) {4.a)} 
		%~ \put (68,27) {4.b)} 
	\end{overpic}
\caption{Virtual avatars in various scenarios demonstrated in our conference paper.}
		   \label{fig:robots_old}
\end{figure}

@@

\begin{figure}
  \centering
  %~ \includegraphics[width=0.6\linewidth]{figures/stair_robust}
  \begin{overpic}[width=0.5\linewidth]{figures/stair_robust}
		\put (17,5) {\small{\color{red}$b_0 = 0.23$}} 
		\put (79,5) {\small{\color{green}$b_0 = 6.16$}} 
		%~ \put (68,) {3.a)} 
		%~ \put (5,27) {3.b)} 
		%~ \put (37,27) {4.a)} 
		%~ \put (68,27) {4.b)} 
	\end{overpic}
  \caption{
           Evaluation of the robustness $b_0$ of two contact configurations. Although in equilibrium, the left configuration is on the verge of slipping.}
		   \label{fig:stair_comp}
\end{figure}

@@

\subsubsection{HRP-2 -- Car egress (Figure~\ref{fig:car}):}
This scenario is inspired from the Darpa challenge car egress scenario (\url{http://cpc.cx/edH}). HRP-2 has 
to find the contact sequence that allows it to step out of a car.

\begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{figures/car}
  \caption{
           Selected frames the car egress scenario. }
		   \label{fig:car}
\end{figure}

\noindent\textbf{Heuristics:} $h_w$.

\noindent\textbf{Observations:} The difficulty of this scenario lies in the strong reduction of the reachable workspace induced 
by the extreme proximity of all obstacles. The planner is able to find a sequence, that consists in many stances.
The proximity of the obstacles invalidate a large number of contact candidates because of collisions. To respect the condition
that only one contact must be broken between each phase, the motion has to be decomposed into a large number of stances (61 in average).
While this scenario is the slower to solve, the planner still computes a solution interactively.
 % \adnote{Maybe define what you mean by 'interactive' and 'real-time' at some point.}

@@

\subsubsection{HyQ -- Obstacle race (Figure~\ref{fig:HyQ_bridge} and~\ref{fig:HyQ_obs}):}
In this long scene, HyQ is first required to cross a 55-cm large hole; then, to cross a narrow ``bridge'', large of only 25-cm.

@@

\noindent\textbf{Observations:} Despite the apparent simplicity of the scene, this scenario is a hard case for a contact planner.
While finding a guide path above the hole is easy for the guide planner, finding a sequence of contacts that allows for equilibrium is not trivial.
Second, the narrow bridge is hard both for the planner and the contact generator: to make sure that equilibrium is preserved along the traversal,
the bridge must be approached with the right angle.
The difficulty is illustrated in Figure~\ref{fig:HyQ_obs}, where several feet rearrangements are required to cross the hole (although the video shows this best).
The planner however succeeds in finding a feasible sequence in the end, again with interactive computation times.

\subsubsection{HRP-2 -- Path re-planning (Figure~\ref{fig:re-planning}):}
In this long scene, HRP-2 plans a path through several obstacles. the scene is edited during the execution of the motion: a stair is added,
some stepping stones are removed, and part of the final staircase is deleted. All these modifications require re-planning.

@@

\begin{table*}
\centering
\footnotesize
\begin{tabular}{ >{\centering\arraybackslash}m{37pt} | >{\centering\arraybackslash}m{57pt} | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{70pt} | >{\centering\arraybackslash}m{73pt} | >{\centering\arraybackslash}m{80pt} | >{\centering\arraybackslash}m{10pt}}
  Scenario (nb steps) &  Complete guide generation & Static equilibrium & Collision & Inverse Kinematics  & Total generation time & Time per step\\
 \hline
   Stairs (18) & 6 -- \textbf{13} --  24 & 13 --  \textbf{32} -- 329   & 1 --  \textbf{4} -- 38 & 26 --  \textbf{127} -- 1345 & 92 --  \textbf{261} -- 2174 & \textbf{14} \\
   Standing (24)& 4 -- \textbf{451} --  985 & 27 --  \textbf{144} -- 338   & 2 --  \textbf{12} -- 37 & 144 --  \textbf{1046} -- 2374 & 310 --  \textbf{1622} -- 3429 & \textbf{66}  \\
   Car (61)& 1 -- \textbf{529} --  995 & 64 --  \textbf{85} -- 144   & 394 --  \textbf{735} -- 1422 & 3947 --  \textbf{13069} -- 36262 & 6775 --  \textbf{20890} -- 52963 & \textbf{342} \\
   Rubble (71)& 3 -- \textbf{524} --  993 & 242 --  \textbf{511} -- 3480   & 233 --  \textbf{505} -- 4564 & 180 --  \textbf{414} -- 3518 & 1400 --  \textbf{30} -- 13126 & \textbf{43} \\
   Race (112)& 1 -- \textbf{501} --  995 & 266 --  \textbf{449} -- 3956   & 824 --  \textbf{1061} -- 2130 & 666 --  \textbf{874} -- 1613 & 2530 --  \textbf{3722} -- 10030 & \textbf{33}
   %Standing up & $70$ & 23 & 48\\
 \end{tabular}
\caption{minimum, \textbf{average} and worst time (in ms) spent in the generation process for each scenario and each critical part of the generation process. The last
column indicates the average time necessary to compute one contact transition.}
\label{tab:requestime}
\quad
\end{table*}

\begin{table*}
\centering
\begin{tabular}{ l | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{65pt} | c}
  &  Path planning & True feasibility & Kinematic failure & Equilibrium failure \\
 \hline
   Steep stairs & 100\%  & 99.5\% & 0.11\% & 0.39\% \\
   Standing up & 68\% & 88\% & 6\% & 6\% \\
   Car egress & 39\% & 77\% & 21\% &  2\% \\
   Rubble & 74\% & 97.87\% & 0.13\% & 2\% \\
   Obstacle race & 58\% & 95.7\% & 1.8\% & 2.5\% \\
 \end{tabular}
\caption{Success rates for each scenario. The first value indicates the percentage of successful complete contact plannings for 1000 tests; The second value
indicates the percentage of truly feasible root configurations: considering each limb individually, indicates the percentage of root placements of the guide trajectory that
led to a feasible contact. Kinematic failure is the percentage of contact generations that failed because no collision-free candidate was found. Equilibrium failure is the percentage of contact
generations that failed because no candidate respected the static equilibrium condition.}
\label{tab:requestpercent}
\quad
\end{table*}

@@

Considering the repartition of the computation time, for HRP-2, most of the time is spent performing inverse kinematics.
This is not surprising considering the number of calls to the methods: IK projection is used intensively to maintain contact continuity between two postures; 
it is also applied every time a new candidate needs to be evaluated. In particular for the car egress scenario,
the kinematic constraints are really strong. Therefore a large number of projections fail because of joint limits violation.

@@

Table~\ref{tab:requestpercent} summarizes the success rates obtained for each scenario.

\subsubsection{Success rates}
We observe that, as expected, our planner does not succeed systematically, because of the approximations made in the implementation
of our theoretical formulation. The extreme situation of the car egress scenario provides the less satisfying results in terms of kinematic failure. This is not
suprising considering the narrowness of the scene.
From a pragmatic point of view, regarding the computation times, we claim that our approach provides a satisfying compromise between completeness and efficiency.
Indeed, the advantage of the framework is that when the contact generation fails, it does so rapidly, which allows us to rapidly re-plan a new contact sequence with a reasonable chance of success.
The most efficient (and immediate) approach is probably to launch in parallel several instances of the planner for a given problem (our current implementation is single threaded) and to apply any successful result.

### 2016-01-03 main.tex
citation tedrake
final version before video inclusion

\author{Steve Tonneau\affilnum{1}, Andrea Del Prete\affilnum{1}, Julien Pettr\'e\affilnum{2}, Nicolas Mansard\affilnum{1}}
 %~ Franck Multon\affilnum{3},
\affiliation{\affilnum{1}LAAS-CNRS, Toulouse, France\\
\affilnum{2}Inria, Rennes, France } % \\
%~ \affilnum{3}Universit\'e Rennes 2, France}

@@

\section{Introduction}
\input{body/intro}
\input{body/overview}
\input{body/rbprm}
\input{body/contact}
\input{body/equilibrium}
\input{body/efort}
\input{body/results}
\input{body/conclusion}
\theendnotes
\bibliographystyle{SageH}
\bibliography{biblio}
\appendix
\input{body/appendix_roms}
\input{body/appendix_algo}
\input{body/appendix_hpp}
\end{document}

>>>>

\author{Steve Tonneau\affilnum{1}, Andrea Del Prete\affilnum{1}, Julien Pettr\'e\affilnum{2}, Chonhyon Park\affilnum{3}, Dinesh Manocha\affilnum{3}, Nicolas Mansard\affilnum{1}}
 %~ Franck Multon\affilnum{3},
\affiliation{\affilnum{1}LAAS-CNRS, Toulouse, France\\
\affilnum{2}Inria, Rennes, France\\
\affilnum{3}UNC, Chapel Hill, USA  } % \\
%~ \affilnum{3}Universit\'e Rennes 2, France}

@@

\section{Introduction}
\input{body/intro}
\input{body/overview}
\input{body/rbprm}
\input{body/contact}
\input{body/equilibrium}
\input{body/efort}
\input{body/results}
\input{body/conclusion}
\section*{Acknowledgements}
This research is supported by Euroc (project under FP7 Grant Agreement  608849),  Entracte (ANR  grant  agreement  13-CORD-002-01),
the ARO Contract W911NF-14-1-0437,
the NSF award 1305286, and a grant from Boeing.
\theendnotes
\bibliographystyle{SageH}
\bibliography{biblio}
\appendix
\input{body/appendix_roms}
\input{body/appendix_algo}
\input{body/appendix_hpp}
\end{document}
